A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-11 paper/elsarticle/elsarticle-template.tex
paper

We propose a spatial AR system for planar scenes that produces the effect of keystone correction analytically, and that facilitates placement by enabling intuitively placing the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera facing downwards towards the scene plane. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling factory floor augmentation exceeding the bounds of the projector's own immediate field of view, using only a single projector.
\end{abstract}

@@

An early spatial AR system for using a projector with a steerable mirror is the IBM Everywhere Displays prototype of Pinhanez \cite{pinhanez2001everywhere}, yet carry out keystone correction manually. Rather than rely on a steerable mirror to support spatial AR to multiple locations using a single projector, some works mount the projector and a camera on a rigid rig and subject the rig to motion \cite{ehnes2004projected,borkowski2004spatial,butz2006applying}. Steering only a mirror, however, places humbler requirements on the system from a hardware standpoint than if an entire camera-projector rig is to be subject to steering. ...

>>>>

We propose a spatial AR system for planar scenes that produces the effect of keystone correction analytically. Our system does so in a manner that facilitates placement by enabling intuitively placing the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera facing downwards towards the scene plane, and reasoning about the dimensions of the projected augmentations in metric terms. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling factory floor augmentation exceeding the bounds of the projector's own immediate field of view, using only a single projector.
\end{abstract}

@@

Keystone correction for planar scenes can be carried out using a 2D homography \cite{Hartley2004}---an invertible transformation that preserves colinearity---and is ultimately the approach we take as well. One approach to calibrating a projector-camera system using a homography reduces to automatically establishing keypoint matches between the image to be projected in the projector's image plane and the projected image in the camera's image plane, and then to use those matches to automatically compute the homography that warps the one image to the other \cite{sukthankar2001smarter}. While such an approach could be extended to enable placement to multiple locations in accordance with a steerable mirror, using keypoint matches alone does not enable reasoning about the target dimensions of augmentations in metric terms.

An early system explicitly using a projector with a steerable mirror is the IBM Everywhere Displays prototype of Pinhanez \cite{pinhanez2001everywhere}; the system, however, has keystone correction carried out manually. Rather than rely on a steerable mirror to support spatial AR to multiple locations using a single projector, some works mount the projector and a camera on a rigid rig and subject the rig to motion \cite{ehnes2004projected,borkowski2004spatial,butz2006applying}. Steering only a mirror, however, places humbler requirements on the system from a hardware standpoint than if an entire camera-projector rig is to be subject to motion.
